Finding Maximum $k$-Cliques Faster \\ Using Lazy Global Domination

### 2016-07-08 talk/talk.tex
Extra line
More on work stealing
Typo
Some tweaks

\begin{frame}{But Is This Practical?}
    \begin{itemize}
        \item We probably want to work with large sparse graphs as inputs.
        \item There are many good maximum clique algorithms for large sparse graphs.
        \item But $G^k$ is large and dense!
        \item There are also good maximum clique algorithms for small dense graphs, but small dense
            graphs can be \emph{very} hard.
            \begin{itemize}
                \item $\omega(\operatorname{G}(500, 0.9))$ can't be solved in a CPU-decade.
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{The Good News}
    \begin{itemize}
        \item Start with a state-of-the-art maximum clique algorithm for small dense graphs.
        \item Replace cubic preprocessing and inference with cheaper quadratic algorithms.
        \item Spend some time making sure the $G^k$ reduction fast.
        \item Buy a hefty amount of RAM.
    \end{itemize}
\end{frame}

@@

            \draw [edge] (Nb) -- (N1);
            \draw [edge] (Nb) -- (N3);
            \draw [edge] (Nb) -- (N5);
        \end{scope}
    \end{tikzpicture}
\end{frame}

@@

\begin{frame}{What About Parallel Search?}

    \begin{itemize}
        \item Active research topic for maximum clique.
            \begin{itemize}
                \item Work stealing strategies really make a huge difference (often more so than
                    load balance)!
                \item Use parallelism to steal early, where value ordering heuristics are
                    weakest---a bit like discrepancy search or restarts.
            \end{itemize}
    \end{itemize}
\end{frame}

@@

@@

\begin{frame}{Conclusion}

    \begin{itemize}
        \item There are many clique relaxations (density-based, degree-based, distance-based,
            \ldots). It's often not clear which you'd want in practice.
        \item $k$-Clique tends to be easy to calculate, at least.
        \item Usually the $k$-Clique and $k$-Club numbers are the same, too.
        \item The domination rule is probably useful in other settings.
        \item Work-stealing strategies matter when doing parallel search.
    \end{itemize}
\end{frame}

>>>>

\begin{frame}{But Is This Practical?}
    \begin{itemize}
        \item We probably want to work with large sparse graphs as inputs.
        \item There are many good maximum clique algorithms for large sparse graphs.
        \item But $G^k$ is large and dense!
        \item There are also good maximum clique algorithms for small dense graphs, but small dense
            graphs can be \emph{very} hard.
            \begin{itemize}
                \item $\omega(\operatorname{G}(500, 0.9))$ can't be solved in a CPU-decade.
            \end{itemize}
        \item It's well known in the CP community that reduction to clique is a bad way of solving
            things.
            \begin{itemize}
                \item (This is not necessarily true, but it's well known\ldots)
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{The Good News}
    \begin{itemize}
        \item Start with a state-of-the-art maximum clique algorithm for small dense graphs.
        \item Replace cubic preprocessing and inference with cheaper quadratic algorithms.
        \item Spend some time making the $G^k$ reduction fast.
        \item Buy a hefty amount of RAM.
    \end{itemize}
\end{frame}

@@

            \draw [edge] (Nb) -- (N1);
            \draw [edge] (Nb) -- (N3);
            \draw [edge] (Nb) -- (N5);

            \draw [edge, dotted] (Na) to [out=-15, in=195] (Nb);
        \end{scope}
    \end{tikzpicture}
\end{frame}

@@

\begin{frame}{What About Parallel Search?}
    \begin{itemize}
        \item Active research topic for maximum clique.
            \begin{itemize}
                \item Work stealing strategies really make a huge difference (often more so than
                    load balance)!
            \end{itemize}
        \item In this paper:
            \begin{itemize}
                \item Dynamic work splitting, starting at the top, and working downwards.
                \item Use parallelism to steal early, where value ordering heuristics are
                    weakest---a bit like discrepancy search or restarts.
            \end{itemize}
    \end{itemize}
\end{frame}

@@

\begin{frame}{Slide of Blatant Propaganda}
    \begin{itemize}
        \item This technique is the only known practical way of getting:
            \begin{itemize}
                \item Reproducible runtimes.
                \item Guarantees of no (exponential) slowdown over sequential, or when adding cores.
                \item Decent work distribution.
                \item Respectable speedups in practice.
            \end{itemize}
        \item I personally think these properties are all critical for practical multi-core parallel
            search.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Conspicuously Missing From This Paper}
    \begin{itemize}
        \item Parallel $G^k$ construction.
        \item Predicting $G(n, p)^k$ on random graphs.
        \item So just why are $G^k$ graphs so easy to solve, anyway?
    \end{itemize}
\end{frame}

\begin{frame}{Conclusion}
    \begin{itemize}
        \item There are many clique relaxations (density-based, degree-based, distance-based,
            \ldots). It's often not clear which you'd want in practice.
        \item $k$-Clique tends to be easy to calculate, at least.
        \item Usually the $k$-Clique and $k$-Club numbers are the same, too.
        \item The domination rule is probably useful in other settings.
        \item Work-stealing strategies matter when doing parallel search.
    \end{itemize}
\end{frame}
